
\cvsection{Other Activities}
\begin{itemize}
    \item Organized Arduino Day Hackathon in BVP, New Delhi.
    \item Organized and managed Tensorflow Watch Party and ML Hackathon.
    \item Organized LFR 2.0 in Evoluzione Fest by ISTE
\end{itemize}
% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}

\cvsection{Projects}

\cvproject{Autonomous Gym}
\begin{itemize}
\item A system to detect whether a user is performing a exercise properly by identifying key-points on the user's body and comparing it to a seed video.
\item Used posture detection implemented in Tensorflow.
\item Provided real-time feedback on any mistake in performance of any exercise. 
\item Capable of detecting posture of multiple persons in a single frame
\end{itemize}

\smallskip
\smallskip

\cvproject{Attendance System Using Face Recognition}
\begin{itemize}
\item An attendance system that uses face detection using OpenCV in python. The system marks the time of entry and time of exit 
\end{itemize}
\smallskip
\smallskip

\cvproject{Mountain Hike}
\begin{itemize}
\item A driving assistant that gives a driver accurate picture of other cars in a radius of few hundred metres
\item Used the concept of indoor localization to vehicles.
\item Used deep learning to detect objects on road other than cars
\item The system suggests appropriate reaction on basis of road condition in case of potential accident situation.
\end{itemize}


\smallskip
\smallskip


\cvproject{Parking Spot Detection and Alert}
\begin{itemize}
\item Developed a system to detect available parking spaces in parking lots as well as authorized parallel parking using existing cameras.
\item Different camera angle, position, image quality, illumination and type of occlusion were the major challenges.
\end{itemize}

\smallskip
\smallskip

\cvproject{Drone Surveillance System}
\begin{itemize}
\item Developed a system to monitor autonomous drones in real time in a region using CNN.
\item Provide safety against malicious use of UAVs using hardware.
\item Provide platform for path planning and registration of drones using blockchain. 
\end{itemize}

\cvproject{}